Starspots on sub sub giants

### 2018-12-05 document/ms.tex
Fixed the latex compilation bug-- needed an obscure usepackage toggle; update outline with progress and content

\usepackage{graphicx}
\usepackage{subfigure}
%\usepackage{lineno}
%\usepackage{blindtext}
%\linenumbers
%\usepackage{breqn}
\usepackage{amsmath}

@@

% \begin{figure*}[h]
%   \centering
%   \begin{tabular}{c}
%     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m119.pdf}}
%     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m118.pdf}} &
%     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m116.pdf}} \\
%     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m114.pdf}} &
%     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m113.pdf}} &
%     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m110.pdf}} \\
%     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m109.pdf}} &
%     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m107.pdf}} &
%     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m106.pdf}}
%   \end{tabular}
% \caption{2-dimensional distributions of filling factor and spot temperature for the nine accepted IGRINS orders for S1063. The median filling factor across these nine orders is $32 \pm 7$\% with a spot temperature of $4000\pm200$ K. As the IGRINS spectrum was observed at maximum light, these show a lower limit on the total spot coverage fraction. }
% \end{figure*}

>>>>

\usepackage{graphicx}
\usepackage[caption=false]{subfig}
%\usepackage{lineno}
%\usepackage{blindtext}
%\linenumbers
%\usepackage{breqn}
\usepackage{amsmath}

@@

 \begin{figure*}[h]
   \centering
   \begin{tabular}{ccc}
     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m119.pdf}} &
     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m118.pdf}} &
     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m116.pdf}} \\
     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m114.pdf}} &
     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m113.pdf}} &
     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m110.pdf}} \\
     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m109.pdf}} &
     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m107.pdf}} &
     \subfloat{\includegraphics[width=2in]{figures/H_band_Tspot_fillingfactor_m106.pdf}}
   \end{tabular}
 \caption{2-dimensional distributions of filling factor and spot temperature for the nine accepted IGRINS orders for S1063. The median filling factor across these nine orders is $32 \pm 7$\% with a spot temperature of $4000\pm200$ K. As the IGRINS spectrum was observed at maximum light, these show a lower limit on the total spot coverage fraction. }
 \end{figure*}
